---
title: "Tootgrowth Analysis"
author: "Rolf Eleveld"
date: "Monday, May 25, 2015"
output: word_document
---

#analysis of tooth growth data
Generic analysis of toothgrowth data

##processing data
Loading data
```{r, ech0=FALSE}
library(UsingR)
data(ToothGrowth) 
```

Initial analysis of tooth growth
```{r}
dim(ToothGrowth)
```
Contains 3 dimensions and 60 findings in total

```{r}
names(ToothGrowth)
```
"len", "supp", and "dose" are column names

Getting a summary
```{r}
summary(ToothGrowth)
```
There are 2 levels on the Supplement

##histograms
Seeing a histogram of the values
```{r}
par(mfrow = c(1, 3))
hist(ToothGrowth$len)
hist(ToothGrowth$dose)
```

Looks like dose is discrete as well
```{r}
unique(ToothGrowth$dose)
```
We see there are 3 unique values here.

Looks like the data uses 2 segments for treatment with a supplement and having 3 doses on each.
lets see each one separate as a confidence interval
##Confidence and p-values
```{r}
#treatment on OJ
X0<-ToothGrowth[ToothGrowth$supp=="OJ",c(1,3)]
#treatment on VC
Y0<-ToothGrowth[ToothGrowth$supp=="VC",c(1,3)]
summary(lm(X0$len ~ X0$dose))
summary(lm(Y0$len ~ Y0$dose))
```

Both show very small p values hence without knowing what the supplement was I can say that there is very little support for this study to take the supplement for growth of teeth.

##Plot of supplement "OJ"
```{r, echo=FALSE, fig.height=6, fig.width=6}
g <- ggplot(data = X0, aes(x = len)) 
g <- g + geom_histogram(aes(y = ..density..), fill = "lightblue", binwidth=1, colour = "black")
g <- g + geom_density(size = 2, colour = "black")
g
```

##Plot of supplement "VC"
```{r, echo=FALSE, fig.height=6, fig.width=6}
g <- ggplot(data = Y0, aes(x = len)) 
g <- g + geom_histogram(aes(y = ..density..), fill = "lightblue", binwidth=1, colour = "black")
g <- g + geom_density(size = 2, colour = "black")
g
```
